Application-Level Regression Testing Framework using Jenkins

### 2017-03-24 manuscript/manuscript.tex
Minor headings restructuring. Also a work in progress for the HTTPD section.

Jenkins is typically available from the package repository of most major linux distribution of choice. One can also download and install Jenkins directly from its website. We used the RPM package to install Jenkins on a CentOS virtual machine (VM). Jenkins comes with its own web server so that managing and accessing Jenkins can be done via any web browser (in the next section we discuss using Apache HTTP Server in front of Jenkin's for better security). Typically Jenkins's web server listen to port 8080, but this is configurable.

Jenkins has an implicit assumption that the machine on which it is installed is also the primary machine being used to build and test the software. In our case, this is not what we would want. In fact, our applications will be built on the HPC system on which we intent to run the tests (typically on the login nodes), and will be run on the compute nodes of the HPC system (i.e. via batch job submission to the job queueing system). This is because not only we want to test the runtime performance of the applications, but also we want to ensure that the software and programming environment of the system can still build the applications correctly. Incidentally, the latter also informs us any user-level problem such as slow or overloaded login nodes, slow file system access, erroneous or incompatible default software (library, compilers, etc) versions. In short, we want our tests to simulate typical workflow of a user on the system being testing.

@@

\subsection{Using Nodes for Test Systems}
The original idea behind adding nodes is to allow Jenkins to scale with the workload it has to do. As projects are added, one can add nodes (i.e. more build machines) allowing Jenkins to build more projects concurrently. Jenkin's project can also be explicitly 'labeled' to only be executed on a certain node. We capitalized both of these features to enable the aforementioned remote execution.

@@

\subsection{Using SSH Plugins for Test Systems}
The SSH plugin (FIXME: Need references) is another method for which one can access the HPC systems from Jenkins. As the name implies, Jenkins project with this type of build scripts simply SSH to the desired machine then execute the scripts there.

@@

>>>>

\subsection{Installation}
Jenkins is typically available from the package repository of most major linux distribution of choice. One can also download and install Jenkins directly from its website. We used the RPM package to install Jenkins on a CentOS virtual machine (VM). Jenkins comes with its own web server so that managing and accessing Jenkins can be done via any web browser (in the next section we discuss using Apache HTTP Server in front of Jenkin's for better security). Typically Jenkins's web server listen to port 8080, but this is configurable.

\subsection{Accessing HPC Test Systems}
Jenkins has an implicit assumption that the machine on which it is installed is also the primary machine being used to build and test the software. In our case, this is not what we would want. In fact, our applications will be built on the HPC system on which we intent to run the tests (typically on the login nodes), and will be run on the compute nodes of the HPC system (i.e. via batch job submission to the job queueing system). This is because not only we want to test the runtime performance of the applications, but also we want to ensure that the software and programming environment of the system can still build the applications correctly. Incidentally, the latter also informs us any user-level problem such as slow or overloaded login nodes, slow file system access, erroneous or incompatible default software (library, compilers, etc) versions. In short, we want our tests to simulate typical workflow of a user on the system being testing.

@@

\subsubsection{Using Nodes for Test Systems}
The original idea behind adding nodes is to allow Jenkins to scale with the workload it has to do. As projects are added, one can add nodes (i.e. more build machines) allowing Jenkins to build more projects concurrently. Jenkin's project can also be explicitly 'labeled' to only be executed on a certain node. We capitalized both of these features to enable the aforementioned remote execution.

@@

\subsubsection{Using SSH Plugins for Test Systems}
The SSH plugin (FIXME: Need references) is another method for which one can access the HPC systems from Jenkins. As the name implies, Jenkins project with this type of build scripts simply SSH to the desired machine then execute the scripts there.

@@

\subsection{Securing Jenkins Web Front-end}

Jenkins comes with its own web server. Although Jenkins also has a command-line interface, the primary way to interact with Jenkins (configuring, setting up projects, running builds) is via a web browser. Although Jenkins web server may be sufficient for a setup in which Jenkins is only accessible in a secure, walled of, intranet environment, we feel that using a more secure, well-tested, production quality web server as its front end is warranted.

We decided to use Apache HTTPD Server as the front-end web server facing the world. To achieve that, first we set Jenkins web server to only listen to \texttt{localhost} interface on port 8080, by setting the following variable in Jenkins configuration file \texttt{/etc/sysconfig/jenkins}:
FIXME: COPY RELEvANT JENKINS CONFIG HERE

Second, we need to forward all HTTP requests to Jenkins, and also forward Jenkins responses back to the client. This is a feature called ''ReverseProxy`` in Apache HTTPD. Th
